\documentclass{article}

\input{preamble.tex}

\begin{document}
\begin{lettergroup}{A}
  \begin{lemma}{adi}{HL}{v}{}
    \sense{\subj{} takes as transport a vehicle such as a boat or plane that is large enough to move around somewhat freely inside}
    \sense{\subj{} takes \obj{} as transport; \obj{} is a boat etc.}
    \begin{derivlemma}{adissa}{HL}{v}
      \sense{\subj{} is located; \subj{} is a boat etc.}
      \sense{\obl{} possesses \obj{}; \obj{} is a boat etc.}
    \end{derivlemma}
    \begin{derivlemma}{adimi}{HL}{v}
      \onesense{\subj{} drives or controls \obj{}; \obj{} is a boat etc.}{}
    \end{derivlemma}
  \end{lemma}
  \begin{lemma}{ado}{L}{v}{}
    \onesense{\subj{} gives \comp{} as a name to \obj{}}{}
    \begin{derivlemma}{adoja}{HL}{n}
      \onesense{a name, esp.\ of people}{}
    \end{derivlemma}
  \end{lemma}
  \begin{lemma}{aeka}{HL}{v}{}
    \sense{time passes}
    \sense{\subj{} passes; \subj{} is one or more intervals of time}
  \end{lemma}
  \begin{lemma}{ago}{L}{v}{}
    \sense{\subj{} puts in effort, does labour, works at something}
    \sense{\subj{} works at or puts in effort towards \obj{}; \obj{} is an activity or task}
  \end{lemma}
  \begin{lemma}{atta}{L}{vs}{}
    \sense{the weather is hot, it is hot out}
    \sense{\subj{} is hot; \subj{} is a volume of space or period of time}
  \end{lemma}
\end{lettergroup}\begin{lettergroup}{D}
  \begin{lemma}{dak-}{L}{v}{}
    \sense{\subj{} is located; \subj{} is a small, hand-sized block such as a brick}
    \sense{\subj{} moves \obj{}; \obj{} is a block etc.}
    \sense{\subj{} moves; \subj{} is a block etc.}
    \sense{\obl{} possesses \obj{}; \obj{} is a block etc.}
  \end{lemma}
  \begin{lemma}{de}{H}{v}{}
    \onesense{\subj{} asks \obl{} \obj{}/\comp{}; \obj{} or \comp{} is a question}{}
  \end{lemma}
  \begin{lemma}{dega}{HL}{v}{}
    \onesense{\subj{} wears \obj{}; \obj{} is a ring or other small cylindrical item worn by inserting a body part into}{}
  \end{lemma}
  \begin{lemma}{dek-}{LH}{vs}{}
    \onesense{\subj{} is standing; \subj{} is a human or other bipedal animal (or physical imitation of such)}{}
    \begin{derivlemma}{dekv-}{LH}{v}
      \onesense{\subj{} stands \obj{} up; \obj{} is a human etc.}{}
    \end{derivlemma}
  \end{lemma}
  \begin{lemma}{dema}{HL}{v}{}
    \sense{\subj{} is located; \subj{} is a large flat display like a monitor or televison screen}
    \sense{\subj{} moves \obj{}; \obj{} is a monitor etc}
    \sense{\subj{} moves; \subj{} is a monitor etc}
    \sense{\obl{} possesses \obj{}; \obj{} is a monitor etc}
  \end{lemma}
  \begin{lemma}{dise}{HL}{vs}{}
    \onesense{\subj{} is broken, \subj{} is nonfunctional, especially due to physical damage; \subj{} is a mechanical or electronic device}{}
    \begin{derivlemma}{disev-}{HL}{v}
      \onesense{\subj{} breaks \obj{} and renders it nonfunctional; \obj{} is a mechanical or electronic device}{}
    \end{derivlemma}
  \end{lemma}
  \begin{lemma}{dixu}{L}{v}{}
    \onesense{\subj{} finds or obtains \obj{}, especially without specifically searching for \obj{}}{}
  \end{lemma}
  \begin{lemma}{don-}{L}{v}{}
    \onesense{\subj{} drinks \obj{}}{}
  \end{lemma}
  \begin{lemma}{duka}{L}{v}{}
    \onesense{\subj{} takes \obj{} from \obl{} without permission, \subj{} steals \obj{} from \obl{}}{}
  \end{lemma}
  \begin{lemma}{dysse}{HL}{v}{}
    \onesense{\subj{} moves in a visually pleasing manner, \subj{} dances}{}
  \end{lemma}
\end{lettergroup}\begin{lettergroup}{E}
  \begin{lemma}{e}{H}{v}{}
    \sense{\subj{} eats \obj{}}
    \sense{\subj{} eats the meal associated with \obj{}; \obj{} is a time of day}
  \end{lemma}
  \begin{lemma}{eno}{HL}{n}{}
    \sense{tea leaf, tea leaves}
    \sense{tea}
  \end{lemma}
  \begin{lemma}{enosamma}{HL}{n}{\begin{etym}\etymtype{compound} of \etymlem{eno}{tea} and \etymlem{samma}{leaf}\end{etym}}
    \onesense{a tea leaf or leaves}{}
  \end{lemma}
  \begin{lemma}{eru}{HL}{v}{}
    \sense{\subj{} passively shows or demonstrates \obj{}}
    \sense{\subj{} shows or demonstrates that \comp{} is true / is the case}
    \begin{derivlemma}{eruv-}{HL}{v}
      \onesense{\subj{} actively points out \obj{} to \obl{}, \subj{} takes \obl{}'s attention and directs it to \obj{}}{}
    \end{derivlemma}
    \begin{derivlemma}{eruja}{HL}{v}
      \onesense{a window, a panel, a diagram, etc.; a defined area which contains a graphical display of information}{}
    \end{derivlemma}
  \end{lemma}
  \begin{lemma}{ete}{H}{n}{}
    \onesense{a house, a home, a building or set of rooms someone lives in}{}
  \end{lemma}
\end{lettergroup}\begin{lettergroup}{G}
  \begin{lemma}{get-}{H}{vs}{}
    \onesense{\subj{} is off, \subj{} is without power; \subj{} is an electrically powered device}{}
    \begin{derivlemma}{getv-}{H}{v}
      \onesense{\subj{} turns \obj{} off, \subj{} disconnects power from \obj{}; \obj{} is an electrically powered device}{}
    \end{derivlemma}
  \end{lemma}
  \begin{lemma}{gimy}{H}{vs}{}
    \onesense{the weather is cool, it is cool out}{}
  \end{lemma}
  \begin{lemma}{gis}{H}{vs}{}
    \onesense{\subj{} sends \obj{} a digital notification or message, \subj{} pings \obj{}, \subj{} calls \obj{}}{}
    \begin{derivlemma}{gisja}{H}{n}
      \onesense{a notification, especially a push notification or similar popup}{}
    \end{derivlemma}
  \end{lemma}
  \begin{lemma}{gyrh-}{L}{v}{}
    \onesense{\subj{} mixes \obl{} into \obj{}, \subj{} mixes \obj{} with \obl{}}{}
    \begin{derivlemma}{gyrhja}{L}{n}
      \sense{a mixing spoon or paddle}
      \sense{a device for mixing, such as a stand mixer}
    \end{derivlemma}
  \end{lemma}
\end{lettergroup}\begin{lettergroup}{H}
  \begin{lemma}{hass-}{LH}{vs}{}
    \onesense{it is raining, the weather is rainy}{}
  \end{lemma}
  \begin{lemma}{hassu}{H}{n}{}
    \onesense{a city, an urban settlement}{}
  \end{lemma}
  \begin{lemma}{hat-}{HL}{v}{}
    \onesense{\subj{} hits or smacks \obj{}}{}
  \end{lemma}
  \begin{lemma}{hete}{L}{v}{}
    \sense{\subj{} is located; \subj{} is a group or mass or pile of packages}
    \sense{\subj{} moves \obj{}; \obj{} is a group etc of packages}
    \sense{\subj{} moves; \subj{} is a group etc of packages}
    \sense{\obl{} possesses \obj{}; \obj{} is a group etc of packages}
  \end{lemma}
  \begin{lemma}{hila}{H}{vs}{}
    \sense{\subj{} is alive; \subj{} is a living being of some kind}
    \sense{with pfv., \subj{} returns to functionality when it had not been functional before; \subj{} is a mechanical or electronic device}
    \begin{derivlemma}{hilav-}{H}{v}
      \sense{\subj{} raises \obj{} from the dead, esp.\ in a Christian sense; \obj{} is (or was) a living being}
      \sense{jokingly, \subj{} restores \obj{} to functionality; \obj{} is a device etc.}
    \end{derivlemma}
  \end{lemma}
  \begin{lemma}{hini}{H}{v}{}
    \sense{\subj{} is located; \subj{} is a flower or other small plant}
    \sense{\subj{} moves \obj{}; \obj{} is a flower etc.}
    \sense{\subj{} moves; \subj{} is a flower etc.}
    \sense{\obl{} possesses \obj{}; \obj{} is a flower etc.}
  \end{lemma}
  \begin{lemma}{hissi}{HL}{vs}{}
    \sense{\subj{} gives off light, \subj{} is bright; \subj{} is a light source}
    \sense{\subj{} is overwhelming or unpleasantly intense}
    \sense{the weather is sunny, it is sunny and bright out}
    \begin{derivlemma}{hissiv-}{HL}{v}
      \sense{\subj{} turns on \obj{}; \obj{} is a light source}
      \sense{\subj{} turns on a light in \obj{}; \obj{} is a room or other space}
    \end{derivlemma}
  \end{lemma}
  \begin{lemma}{ho}{H}{vs}{}
    \onesense{\subj{} is on, \subj{} is energised; \subj{} is an electrically powered device}{}
    \begin{derivlemma}{hov-}{H}{v}
      \onesense{\subj{} turns \obj{} on, \subj{} connects power to \obj{}; \obj{} is an electrically powered device}{}
    \end{derivlemma}
  \end{lemma}
  \begin{lemma}{huru}{LH}{v}{}
    \sense{\subj{} drives a vehicle such as a bicycle or motorcycle, which is ridden by setting oneself across the vehicle with one's legs on either side}
    \sense{\subj{} drives \obj{}; \obj{} is a bicycle etc.}
    \begin{derivlemma}{hurussa}{LH}{v}
      \sense{\subj{} is located; \subj{} is a bicycle etc.}
      \sense{\obl{} possesses \obj{}; \obj{} is a bicycle etc.}
    \end{derivlemma}
    \begin{derivlemma}{huruune}{LH}{v}
      \sense{\subj{} takes a bicycle etc. driven by someone other than \subj{} as transport}
      \sense{\subj{} takes \obj{} as transport; \obj{} is a bicycle etc. driven by someone other than \subj{}}
    \end{derivlemma}
  \end{lemma}
\end{lettergroup}\begin{lettergroup}{I}
  \begin{lemma}{ikke}{H}{v}{}
    \sense{\subj{} is located; \subj{} is a laptop or other large but hand-portable electronic device}
    \sense{\subj{} moves \obj{}; \obj{} is a laptop etc.}
    \sense{\subj{} moves; \subj{} is a laptop etc.}
    \sense{\obl{} possesses \obj{}; \obj{} is a laptop etc.}
  \end{lemma}
  \begin{lemma}{ima}{LH}{n}{}
    \sense{morning, time between about 5 AM and 11 AM}
    \sense{breakfast, the regular morning meal}
  \end{lemma}
  \begin{lemma}{inne}{HL}{vs}{}
    \sense{\subj{} tastes sweet}
    \sense{with PFV; \subj{} becomes sweet, e.g. due to ripening}
    \begin{derivlemma}{innev-}{HL}{v}
      \sense{\subj{} adds a sweet taste to \obj{}}
      \sense{\subj{} allows \obj{} to ripen; \obj{} is a fruit}
      \sense{\subj{} allows \obj{} to sweeten due to malting or kouji enzymes; \obj{} is grain}
    \end{derivlemma}
    \begin{derivlemma}{inne}{HL}{adj}
      \onesense{NOUN is sweet, NOUN has a sweet taste}{}
    \end{derivlemma}
  \end{lemma}
  \begin{lemma}{issa}{HL}{v}{}
    \onesense{\subj{} spends time doing \obj{}; \obj{} is an activity or task}{}
  \end{lemma}
  \begin{lemma}{iti}{H}{v}{}
    \onesense{\subj{} closes \obj{}; \obj{} is a door or swinging lid or other such device that closes by swinging shut}{}
  \end{lemma}
\end{lettergroup}\begin{lettergroup}{J}
  \begin{lemma}{jana}{HL}{v}{}
    \sense{\subj{} sings, \subj{} makes musical noices with \subj{}'s voice}
    \sense{\subj{} sings \obj{}; \obj{} is a song with lyrics}
    \begin{derivlemma}{janaja}{HL}{n}
      \onesense{a microphone, especially a stage mic or other large mic meant for being sung into}{}
    \end{derivlemma}
  \end{lemma}
  \begin{lemma}{jeh-}{H}{v}{}
    \sense{\subj{} sends a digital message (usually text) to \obl{}}
    \sense{\subj{} sends \obj{} as a digital message to \obl{}}
    \sense{\subj{} says \comp{} via a digital text channel}
  \end{lemma}
  \begin{lemma}{jekk-}{L}{vs}{}
    \onesense{\subj{} is clean, \subj{} is free of grime/pathogens and safe to handle}{}
    \begin{derivlemma}{jekkv-}{L}{v}
      \onesense{\subj{} cleans \obj{}, \subj{} removes grime/pathogens from \obj{}}{}
    \end{derivlemma}
  \end{lemma}
  \begin{lemma}{juma}{L}{v}{}
    \onesense{\obl{} considers \obj{}/\comp{} odd or surprising}{}
  \end{lemma}
\end{lettergroup}\begin{lettergroup}{K}
  \begin{lemma}{kata}{H}{v}{}
    \sense{\subj{} takes a train or other large, articulated, guided vehicle as transport}
    \sense{\subj{} takes \obj{} as transport; \obj{} is a train etc.}
    \begin{derivlemma}{katassa}{H}{v}
      \onesense{\subj{} is located; \subj{} is a train etc.}{}
    \end{derivlemma}
    \begin{derivlemma}{katami}{HL}{v}
      \onesense{\subj{} drives or controls \obj{}; \obj{} is a train etc.}{}
    \end{derivlemma}
  \end{lemma}
  \begin{lemma}{ki}{H}{v}{}
    \onesense{\subj{} clicks on \obj{}, \subj{} taps \obj{}; \obj{} is a location or item on a digital display}{}
    \begin{derivlemma}{kija}{H}{n}
      \sense{a mouse or other device used to move a cursor on a digital display and interact with interface elements}
      \sense{the cursor on a digital display}
    \end{derivlemma}
  \end{lemma}
  \begin{lemma}{kjati}{HL}{vs}{}
    \sense{\subj{} tastes sour}
    \sense{with PFV; \subj{} becomes sour esp. due to lactic acid fermentation}
    \begin{derivlemma}{kjativ-}{HL}{v}
      \sense{\subj{} adds a sour taste to \obj{}}
      \sense{\subj{} ferments \obj{} via lactic acid fermentation}
    \end{derivlemma}
    \begin{derivlemma}{kjati}{HL}{adj}
      \onesense{NOUN is sour, NOUN has a sour taste}{}
    \end{derivlemma}
  \end{lemma}
  \begin{lemma}{koja}{H}{v}{}
    \sense{\subj{} is located; \subj{} is a bottle or jar or other tall, narrow cylindrical container}
    \sense{\subj{} moves \obj{}; \obj{} is a bottle etc.}
    \sense{\subj{} moves; \subj{} is a bottle etc.}
    \sense{\obl{} possesses \obj{}; \obj{} is a bottle etc.}
  \end{lemma}
\end{lettergroup}\begin{lettergroup}{L}
  \begin{lemma}{lappa}{LH}{v}{}
    \sense{\subj{} wakes up, \subj{} exits sleep; \subj{} is a living creature}
    \sense{\subj{} returns to full activity mode; \subj{} is an electronic device}
    \begin{derivlemma}{lappav-}{LH}{v}
      \sense{\subj{} wakes up \obj{}; \obj{} is a living creature}
      \sense{\subj{} causes \obj{} to return to full activity mode; \obj{} is an electronic device}
    \end{derivlemma}
  \end{lemma}
  \begin{lemma}{lhimo}{LH}{v}{}
    \onesense{\subj{} decides upon \obj{} / decides to do \comp{}}{}
    \begin{derivlemma}{lhimod-}{LH}{v}
      \onesense{in a situation where a choice was previously discussed or considered, \subj{} acts in such a way that \obj{} / \comp{} is now either the only possible choice or effectively chosen anyway, despite \subj{}'s likely lack of awareness of this effect of their action}{}
    \end{derivlemma}
  \end{lemma}
  \begin{lemma}{lhjarru}{LH}{v}{}
    \sense{\subj{} is located; \subj{} is a piece of jewelry or other small decorative item}
    \sense{\subj{} moves \obj{}; \obj{} is jewelry etc.}
    \sense{\subj{} moves; \subj{} is jewelry etc.}
    \sense{\obl{} possesses \obj{}; \obj{} is jewelry etc.}
  \end{lemma}
\end{lettergroup}\begin{lettergroup}{M}
  \begin{lemma}{mana}{L}{v}{}
    \sense{\subj{} moves a mouse cursor}
    \sense{\subj{} moves \obj{}; \obj{} is a mouse cursor}
    \sense{\subj{} moves; \subj{} is a mouse cursor}
    \begin{derivlemma}{manassa}{L}{v}
      \sense{\subj{} is located; \subj{} is a mouse cursor}
      \sense{\obl{} possesses \obj{}; \obj{} is a mouse cursor}
    \end{derivlemma}
  \end{lemma}
  \begin{lemma}{maro}{HL}{vs}{}
    \sense{\subj{} is dead; \subj{} is a living being of some kind}
    \sense{\subj{} is fully nonfunctional and cannot even attempt to function, \subj{} is bricked; \subj{} is a mechanical or electronic device}
    \begin{derivlemma}{marov-}{HL}{v}
      \sense{\subj{} kills \obj{}; \obj{} is a living being etc.}
      \sense{\subj{} breaks \obj{} and renders it fully nonfunctional, especially by minimal or unexpected means; \obj{} is a device etc.}
      \begin{derivlemma}{marovad-}{HL}{v}
        \onesense{\subj{} accidentally renders \obj{} nonfunctional; \obj{} is a device etc.}{}
      \end{derivlemma}
    \end{derivlemma}
  \end{lemma}
  \begin{lemma}{mir-}{HL}{v}{}
    \onesense{\subj{} says \comp{} orally or audibly}{}
    \begin{derivlemma}{mirja}{HL}{n}
      \sense{language, a language}
      \sense{Mirja, the Mirja language}
    \end{derivlemma}
  \end{lemma}
  \begin{lemma}{mylja}{HL}{n}{}
    \onesense{a store, a place where goods are sold and bought}{}
  \end{lemma}
\end{lettergroup}\begin{lettergroup}{N}
  \begin{lemma}{naggja}{HL}{v}{}
    \sense{\subj{} counts out or measures out \obj{}; \obj{} is a set of discrete items}
    \sense{\subj{} delimits \obj{} into one or more discrete zones; \obj{} is a continuous space}
    \begin{derivlemma}{naggjaja}{HL}{n}
      \onesense{a boundary, a limit, a division in a continuous space}{}
    \end{derivlemma}
  \end{lemma}
  \begin{lemma}{naja}{L}{v}{}
    \sense{\subj{} is located; \subj{} is a large stiff flat object like a countertop or panel}
    \sense{\subj{} moves; \subj{} is a large stiff flat object}
    \sense{\subj{} moves \obj{}; \obj{} is a large stiff flat object}
    \sense{\obl{} possesses \obj{}; \obj{} is a large stiff flat object}
  \end{lemma}
  \begin{lemma}{nega}{LH}{v}{}
    \sense{\subj{} is located; \subj{} is digital audio or video or audiovisual data such as a video file or sound file}
    \sense{\obl{} possesses \subj{}; \subj{} is digital audiovisual data}
    \sense{\obl{} knows \obj{}, \obl{} knows how to do \obj{}; \obj{} is a method or process or action}
  \end{lemma}
  \begin{lemma}{nige}{HL}{v}{}
    \sense{\subj{} is located; \subj{} is a small four-footed animal}
    \sense{\subj{} moves \obj{}; \obj{} is a small animal etc.}
    \sense{\subj{} moves; \subj{} is a small animal etc.}
    \sense{\obl{} possesses \obj{}; \obj{} is a small animal etc.}
  \end{lemma}
  \begin{lemma}{niiv-}{L}{v}{}
    \sense{\subj{} flows; \subj{} is a high-viscosity liquid like honey}
    \sense{\subj{} pours or pushes \obj{}; \obj{} is a liquid etc}
    \sense{\obl{} possesses an uncontained mass of \obj{}; \obj{} is a liquid etc}
    \begin{derivlemma}{niivyssa}{L}{v}
      \onesense{\subj{} is located; \subj{} is an uncontained mass of liquid etc}{}
    \end{derivlemma}
  \end{lemma}
  \begin{lemma}{niko}{LH}{vs}{}
    \sense{\subj{} is happy, content}
    \sense{\obj{} is happy about or likes \obl{}, \obl{} makes \obj{} happy}
  \end{lemma}
  \begin{lemma}{nirrhe}{H}{v}{}
    \sense{\subj{} is located; \subj{} is a non-mechanical tool small enough to be manipulated in one hand (e.g.\ a knife or trowel)}
    \sense{\subj{} moves \obj{}; \obj{} is a small tool etc.}
    \sense{\subj{} moves; \subj{} is a small tool etc.}
    \sense{\obl{} possesses \obj{}; \obj{} is small tool etc.}
  \end{lemma}
  \begin{lemma}{nisa}{LH}{n}{}
    \onesense{a phone, a smartphone, a handheld computing device}{}
  \end{lemma}
  \begin{lemma}{nixxa}{HL}{vs}{}
    \sense{\subj{} is far away from the speaker}
    \sense{\subj{} is far away from \obl{}}
  \end{lemma}
  \begin{lemma}{nyit-}{HL}{v}{}
    \sense{\subj{} is outdoors, \subj{} is not inside a building or other enclosed space}
    \sense{\slz{}, \vb{} is done outdoors}
  \end{lemma}
\end{lettergroup}\begin{lettergroup}{O}
  \begin{lemma}{okko}{H}{v}{}
    \onesense{\subj{} walks or runs; \subj{} is a horse or other similarly-moving animal}{}
  \end{lemma}
\end{lettergroup}\begin{lettergroup}{R}
  \begin{lemma}{rhaka}{LH}{v}{}
    \sense{\subj{} orders \obl{} to perform \obj{}/\comp{}}
    \sense{\subj{} is in authority over \obj{}; with pfv., \subj{} gives an order to \obj{}}
    \begin{derivlemma}{rhakama}{LH}{n}
      \onesense{a commander, a lord, an authority figure with the right to give orders}{}
    \end{derivlemma}
  \end{lemma}
  \begin{lemma}{ryky}{L}{vs}{}
    \sense{\subj{} is located; \subj{} is a book or other bound stack of paper or similar thin sheets}
    \sense{\subj{} moves; \subj{} is a book etc.}
    \sense{\obl{} possesses \obj{}; \obj{} is a book etc.}
    \begin{derivlemma}{rykyva}{L}{v}
      \onesense{\subj{} moves or places \obj{}; \obj{} is a book etc.}{}
    \end{derivlemma}
  \end{lemma}
\end{lettergroup}\begin{lettergroup}{S}
  \begin{lemma}{sama}{H}{v}{}
    \sense{\subj{} tells a story, \subj{} relates a narrative}
    \sense{\subj{} tells or relates \obj{}, \obj{} is a narrative of some kind}
    \sense{\subj{} relates how \comp{} happened, \subj{} depicts \comp{}}
  \end{lemma}
  \begin{lemma}{samma}{L}{n}{}
    \onesense{a leaf or other photosynthetic projection from a plant}{}
  \end{lemma}
  \begin{lemma}{sar-}{H}{v}{}
    \onesense{\obj{} is audible to \obl{}, \obl{} hears or can hear \obj{}}{}
    \begin{derivlemma}{sarv-}{H}{v}
      \onesense{\subj{} listens to \obj{}, \subj{} directs their attention to \obj{}; \obj{} is a noise or the source of a noise}{}
    \end{derivlemma}
  \end{lemma}
  \begin{lemma}{sewa}{HL}{vs}{}
    \sense{\subj{} is low on or out of battery, \subj{} has run out of stored energy; \subj{} is an electrical or electronic device}
    \sense{\subj{} is tired, \subj{} is low on energy; \subj{} is a living being}
  \end{lemma}
  \begin{lemma}{sik-}{H}{v}{}
    \onesense{\subj{} cuts \obj{}, \subj{} divides \obj{} using a knife or similar tool}{}
    \begin{derivlemma}{sikja}{H}{n}
      \sense{with \lem{nirrhe}, a knife, esp.\ of kitchen use size}
      \sense{with \lem{urhu}, a sword or machete or other such large cutting tool}
    \end{derivlemma}
  \end{lemma}
  \begin{lemma}{sima}{HL}{v}{}
    \onesense{\subj{} drives a car or other wheeled vehicle one rides inside but cannot move freely inside}{}
    \begin{derivlemma}{simassa}{H}{v}
      \onesense{\subj{} is located; \subj{} is a car etc.}{}
    \end{derivlemma}
    \begin{derivlemma}{simaane}{HL}{v}
      \sense{\subj{} takes a car etc. driven by someone other than \subj{} as transport}
      \sense{\subj{} takes \obj{} as transport; \obj{} is a car etc driven by someone other than \subj{}}
    \end{derivlemma}
  \end{lemma}
  \begin{lemma}{sinna}{L}{vs}{}
    \onesense{\subj{} is quiet, \subj{} is making little or no noise}{}
    \begin{derivlemma}{sinnav-}{L}{v}
      \onesense{\subj{} causes \obj{} to become quiet; \obj{} is usually but not exclusively an audio output device}{}
    \end{derivlemma}
  \end{lemma}
  \begin{lemma}{siva}{H}{v}{}
    \sense{\subj{} executes \obj{}; \subj{} is an electronic device or piece of software, \obj{} is a program or piece of software}
    \sense{\subj{} performs a pre-scripted activity such as a ceremony or play or cultural script}
  \end{lemma}
  \begin{lemma}{su}{H}{v}{}
    \onesense{\subj{} walks; \subj{} is a human or other biped}{}
  \end{lemma}
  \begin{lemma}{sumu}{L}{vs}{}
    \sense{\subj{} is asleep; \subj{} is a living creature}
    \sense{\subj{} is powered on but in a state of minimal activity pending user input; \subj{} is an electronic device}
    \begin{derivlemma}{sumuv-}{L}{v}
      \sense{\subj{} puts \obj{} to sleep; \obj{} is a living creature}
      \sense{\subj{} puts \obj{} in a state of minimal activity pending further input; \obj{} is an electronic device}
    \end{derivlemma}
  \end{lemma}
  \begin{lemma}{syyte}{HL}{vs}{}
    \sense{\subj{} is waiting}
    \sense{\subj{} is waiting for \obl{}}
    \begin{derivlemma}{syyteva}{HL}{v}
      \onesense{\subj{} pauses \obj{}, \subj{} sets \obj{} aside for the moment}{}
    \end{derivlemma}
  \end{lemma}
\end{lettergroup}\begin{lettergroup}{T}
  \begin{lemma}{taeke}{HL}{vs}{}
    \onesense{\subj{} is boiling}{}
    \begin{derivlemma}{taekeva}{HL}{v}
      \onesense{\subj{} causes \obj{} to boil}{}
    \end{derivlemma}
  \end{lemma}
  \begin{lemma}{tesse}{H}{v}{}
    \onesense{\subj{} runs; \subj{} is a human or other bipedal animal (or physical imitation of such)}{}
    \begin{derivlemma}{tesseja}{H}{n}
      \onesense{a treadmill or other such device for running in place for exercise}{}
    \end{derivlemma}
  \end{lemma}
  \begin{lemma}{tirha}{L}{v}{}
    \sense{\subj{} is located; \subj{} is digital text data}
    \sense{\obl{} possesses \subj{}; \subj{} is digital text data}
    \sense{\obl{} knows \obj{}/\comp{}; \obj{}/\comp{} is a fact or data point}
  \end{lemma}
  \begin{lemma}{tyke}{H}{v}{}
    \sense{\subj{} is located; \subj{} is a mass of small bits such as gravel or beans}
    \sense{\subj{} moves \obj{}; \obj{} is gravel etc.}
    \sense{\subj{} moves; \subj{} is gravel etc.}
    \sense{\obl{} possesses \obj{}; \obj{} is gravel etc.}
  \end{lemma}
  \begin{lemma}{tyro}{L}{n}{}
    \onesense{the news, the happenings, the things that are going on at the moment}{}
  \end{lemma}
\end{lettergroup}\begin{lettergroup}{U}
  \begin{lemma}{ujje}{HL}{vs}{}
    \onesense{\obl{} is frustrated or upset by \obj{}, \obj{} causes \obl{} frustration}{}
  \end{lemma}
  \begin{lemma}{ulhu}{HL}{v}{}
    \sense{\subj{} prepares \obj{}; \obj{} is a meal or completed food item}
    \sense{\subj{} prepares a meal etc.}
    \begin{derivlemma}{ulhuro}{HL}{n}
      \onesense{cooked food, finished meal product, esp.\ pejorative (`cooking was done, at least')}{}
    \end{derivlemma}
  \end{lemma}
  \begin{lemma}{une}{L}{vs}{}
    \onesense{\subj{} is ill, \subj{} is feeling unwell}{}
  \end{lemma}
  \begin{lemma}{urhu}{L}{v}{}
    \sense{\subj{} is located; \subj{} is a non-mechanical tool large enough to require two hands to manipulate naturally (e.g.\ a shovel or broom)}
    \sense{\subj{} moves \obj{}; \obj{} is a large tool etc.}
    \sense{\subj{} moves; \subj{} is a large tool etc.}
    \sense{\obl{} possesses \obj{}; \obj{} is a large tool etc.}
  \end{lemma}
  \begin{lemma}{uru}{L}{v}{}
    \sense{\subj{} is located; \subj{} is a bowl or other bowl-shaped object}
    \sense{\subj{} moves \obj{}; \obj{} is a bowl etc.}
    \sense{\subj{} moves; \subj{} is a bowl etc.}
    \sense{\obl{} possesses \obj{}; \obj{} is a bowl etc.}
  \end{lemma}
  \begin{lemma}{usi}{HL}{vs}{}
    \sense{\subj{} is sad, upset, frustrated, disappointed}
    \sense{\obl{} is sad etc about \obj{}}
  \end{lemma}
  \begin{lemma}{ussa}{H}{v}{}
    \sense{\subj{} moves; \subj{} is a leaf or other small thin and flat light object}
    \sense{\subj{} is located; \subj{} is a leaf etc.}
    \sense{\obl{} possesses \obj{}; \obj{} is a leaf etc.}
    \begin{derivlemma}{ussava}{H}{v}
      \onesense{\subj{} moves or places \obj{}; \obj{} is a leaf etc.}{}
    \end{derivlemma}
  \end{lemma}
\end{lettergroup}\begin{lettergroup}{V}
  \begin{lemma}{va}{irregular (H, but often L before H suffixes)}{prov}{}
    \sense{\subj{} does the aforementioned action, \subj{} does it, \subj{} does that}
    \sense{\subj{} does \obj{}; \obj{} is an action}
    \begin{derivlemma}{-v-}{∅}{dsuff}
      \onesense{derives verbs for actions performed intentionally by \subj{}, or state changes brought about by \subj{}}{}
    \end{derivlemma}
    \begin{derivlemma}{-va}{∅}{dsuff}
      \onesense{derives verbs of causing motion from some location verbs}{}
    \end{derivlemma}
  \end{lemma}
  \begin{lemma}{ven-}{L}{vs}{}
    \onesense{\subj{} is showing \obj{}; \subj{} is a digital display}{}
    \begin{derivlemma}{venav-}{L}{v}
      \onesense{\subj{} causes a digital display to show \obj{}}{}
    \end{derivlemma}
    \begin{derivlemma}{venja}{L}{v}
      \onesense{a screen, a monitor, a digital display of some kind}{}
    \end{derivlemma}
  \end{lemma}
  \begin{lemma}{vimm-}{L}{vs}{}
    \onesense{\subj{} is steeping in or soaking in \obl{}; \obl{} is a liquid or possibly other fluid}{}
    \begin{derivlemma}{vimmav-}{L}{v}
      \onesense{\subj{} causes \obj{} to soak in or steep in \obl{}; \obl{} is a liquid etc}{}
    \end{derivlemma}
  \end{lemma}
  \begin{lemma}{virha}{LH}{v}{}
    \onesense{\subj{} climbs, \subj{} ascends a vertical or near-vertical surface by using all limbs}{}
  \end{lemma}
  \begin{lemma}{vis-}{L}{v}{}
    \sense{\subj{} types text}
    \sense{\subj{} types \obj{}; \obj{} is text}
  \end{lemma}
\end{lettergroup}\begin{lettergroup}{W}
  \begin{lemma}{weje}{HL}{vs}{}
    \onesense{\subj{} is sitting; \subj{} is a human or other bipedal animal (or physical imitation of such)}{}
  \end{lemma}
\end{lettergroup}\begin{lettergroup}{X}
  \begin{lemma}{xagu}{HL}{vs}{}
    \onesense{\subj{} has gone bad, \subj{} is rotten}{}
    \begin{derivlemma}{xaguv-}{HL}{v}
      \onesense{\subj{} ferments \obj{}}{}
    \end{derivlemma}
  \end{lemma}
  \begin{lemma}{xalhhe}{L}{v}{}
    \sense{\subj{} flows; \subj{} is a low-viscosity liquid such as water}
    \sense{\subj{} pours or pushes \obj{}; \obj{} is a liquid etc}
    \sense{\obl{} possesses an uncontained mass of \obj{}; \obj{} is a liquid etc}
    \begin{derivlemma}{xalhhessa}{L}{v}
      \onesense{\subj{} is located; \subj{} is an uncontained mass of liquid etc}{}
    \end{derivlemma}
  \end{lemma}
  \begin{lemma}{xave}{HL}{n}{\begin{etym}\etymtype{portmanteau} of \etymlem{xaguv-}{ferment} and \etymlem{eno}{tea}\end{etym}}
    \onesense{kombucha}{}
  \end{lemma}
\end{lettergroup}\begin{lettergroup}{Y}
  \begin{lemma}{yima}{L}{n}{}
    \onesense{a span of time, a length of time}{}
  \end{lemma}
  \begin{lemma}{yle}{LH}{n}{}
    \onesense{a cup, a mug, a small container for holding liquid to drink from}{}
  \end{lemma}
  \begin{lemma}{ynna}{LH}{vs}{}
    \sense{\subj{} supports \obl{}}
    \sense{\subj{} is a reason behind \obl{}, \subj{} explains \obl{} at least in part}
    \sense{\subj{} is basic, \subj{} is fundamental}
  \end{lemma}
\end{lettergroup}
\end{document}